\documentclass[11pt]{article}

% ======================================================================
% Final results summary for the bruise-segmentation project.
% Source: bruise_colab_final.ipynb + results_final/.
% YOLO = native Ultralytics argmax only. Self-contained (CTAN packages
% only) -> portable Tectonic:
%     tools/tectonic/tectonic.exe docs/final_results_summary.tex
% ======================================================================

\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{array}
\usepackage{caption}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\newcommand{\best}[1]{\textbf{#1}}
\newcommand{\sig}{\textcolor{red!70!black}{\textbf{significant}}}
\newcommand{\ns}{n.s.}
\newcommand{\ci}[2]{[#1,\,#2]}

\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{0.6em}{}
\setlength{\parskip}{0.4em}
\setlength{\parindent}{0pt}

\title{\bfseries Final Results --- Bruise Segmentation}
\author{Injury Analytics Lab}
\date{Source: \texttt{bruise\_colab\_final.ipynb} + \texttt{results\_final/}}

\begin{document}
\maketitle

\noindent\textbf{Test set:} 185 white-light images / 28 subjects (strict
3-labeler intersection), scored against the \textbf{2-of-3 majority vote} on a
common $640\times640$ grid. \textbf{YOLO evaluation:} native Ultralytics
\texttt{.predict()} argmax.\\[0.3em]
\textbf{Metric note:} Dice is strongly bimodal (a model either localizes the
bruise or blanks). \emph{Median} = typical-case quality; \emph{mean} is dragged
down by complete misses; \emph{miss \%} = the safety axis (images with a bruise
where the model predicts \emph{zero} pixels).

% ---------------------------------------------------------------
\section{Accuracy --- test results (185 images)}

\begin{center}
\begin{tabular}{lcccc}
\toprule
Model & Params (M) & Mean Dice & Median Dice & Miss \% \\
\midrule
\best{SegFormer-B2 (teacher)}                 & 27.35 & \best{0.7692} & 0.8192 & \best{0.00} \\
\best{SegFormer-B0 (distilled, $\alpha$=0.6)} & 3.71  & \best{0.7680} & 0.8167 & \best{0.00} \\
SegFormer-B0 (direct)                         & 3.71  & 0.7663 & 0.8129 & 0.54 \\
YOLO26n (distilled, $\alpha$=0.4)             & 1.63  & 0.7261 & 0.8012 & 2.16 \\
YOLO26n (direct)                              & 1.63  & 0.7021 & 0.8061 & 6.49 \\
\bottomrule
\end{tabular}
\end{center}

The three SegFormers are statistically indistinguishable on Dice
($\sim$0.77 mean / $\sim$0.81 median) but separate sharply on \textbf{miss
rate}: the teacher and the distilled student never blank. YOLO's \emph{median}
is competitive ($\sim$0.80) but its \emph{mean} is lower because it blanks on
2--6\,\% of images.

% ---------------------------------------------------------------
\section{External baselines (val-selected best seed --- same policy as the 5 models above)}

\begin{center}
\begin{tabular}{lcccc}
\toprule
Model & Params (M) & Mean Dice & Median Dice & Miss \% \\
\midrule
DeepLabV3+ (ResNet-50)  & 26.68 & 0.7584 & 0.8183 & 2.16 \\
U-Net (ResNet-50)       & 32.52 & 0.7570 & 0.8329 & 3.78 \\
\bottomrule
\end{tabular}
\end{center}

Both baselines are now selected the \textbf{same way as the five core models}
--- highest \emph{validation} Dice across 3 seeds, then that seed's test result
--- so the comparison is symmetric (best-of-3 for everyone). They land just
below the three SegFormers on mean Dice and blank more often; the SegFormer
distilled student remains the best of everything tested and, at 3.71\,M params,
one of the smallest. (U-Net posts the highest \emph{median} Dice of any model,
0.8329, but its larger mean-vs-median gap and 3.78\,\% miss rate reflect more
complete failures.)

% ---------------------------------------------------------------
\section{Speed / latency (640-tensor-on-GPU $\to$ mask, per image)}

Timed inside a double \texttt{cuda.synchronize()}; disk / decode / resize /
copy excluded (identical across models, I/O-dominated).

\begin{center}
\begin{tabular}{lccccc}
\toprule
Model & Median (ms) & p95 (ms) & FPS & Params (M) & Peak act. (MB) \\
\midrule
SegFormer-B2 (teacher)   & 33.67 & 34.95 & 29.7  & 27.35 & 1779 \\
SegFormer-B0 (direct)    & 16.68 & 16.94 & 59.9  & 3.71  & 1204 \\
SegFormer-B0 (distilled) & 16.64 & 17.07 & 60.1  & 3.71  & 1204 \\
YOLO26n (direct)         & 8.18  & 8.36  & 122.2 & 1.63  & 967  \\
YOLO26n (distilled)      & 8.22  & 8.51  & 121.7 & 1.63  & 967  \\
\bottomrule
\end{tabular}
\end{center}

YOLO is $\sim$2$\times$ faster and $\sim$7$\times$ smaller than B2; the B0
student matches the B2 teacher's accuracy at 2$\times$ the teacher's speed.

% ---------------------------------------------------------------
\section{Paired contrasts (subject-level cluster bootstrap)}

$\Delta$ = model A $-$ model B on the same resample. $P(\Delta{>}0)$ is
one-sided.

\begin{center}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lcccc}
\toprule
Contrast & $\Delta$ & 95\% CI & $P(\Delta{>}0)$ & Verdict \\
\midrule
Distillation (B0-dist $-$ B0-direct)   & $+0.0017$ & \ci{-0.009}{+0.013} & 0.58 & \ns \\
Student $-$ teacher (B0-dist $-$ B2)   & $-0.0012$ & \ci{-0.020}{+0.018} & 0.44 & \ns \\
YOLO distilled $-$ direct              & $+0.0239$ & \ci{-0.014}{+0.059} & 0.90 & \ns \\
\best{SegFormer $-$ YOLO (B0-dist $-$ YOLO-dir)} & \best{$+0.0659$} & \ci{+0.011}{+0.121} & 0.994 & \sig \\
\best{Miss \%: YOLO-direct $-$ B0-dist}         & \best{$+6.49$}   & \ci{+2.39}{+11.63}  & 1.00  & \sig \\
\bottomrule
\end{tabular}
\end{center}

At $n{=}28$ subjects, Dice differences between healthy models (distillation,
student-vs-teacher) are smaller than the resolvable effect --- they are null.
What \emph{is} resolvable lives in the \textbf{miss rate} and in the
SegFormer-vs-YOLO gap.

% ---------------------------------------------------------------
\section{Fairness across skin tone (ITA groups)}

Per-image Dice averaged over runs, stratified by 5 ITA groups.
Kruskal--Wallis omnibus + Mann--Whitney (Bonferroni over 10 pairs).
Fairness gap = best $-$ worst group median.

\begin{center}
\begin{tabular}{lccccc}
\toprule
Model & Omnibus $p$ & Sig.? & Dice gap & Worst group & Miss gap \\
\midrule
SegFormer-B2 (teacher)   & 0.011 & \sig & 0.112 & Tan (IV)       & 0.00 \\
SegFormer-B0 (direct)    & 0.638 & \ns  & 0.052 & Dark (VI)      & 0.00 \\
SegFormer-B0 (distilled) & 0.470 & \ns  & 0.050 & Dark (VI)      & 0.00 \\
YOLO26n (direct)         & 0.230 & \ns  & 0.104 & Light (II-III) & 0.154 \\
YOLO26n (distilled)      & 0.151 & \ns  & 0.090 & Light (II-III) & 0.051 \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Only one pairwise comparison survives Bonferroni:} SegFormer-B2
Intermediate (III-IV) vs Dark (VI), $p{=}0.0079$. Everything else is \ns{}
after correction. YOLO's worst group is \textbf{Light}, not Dark --- driven by
a size confound (light-skin bruises are smaller, so more misses) --- and the
intervals are too wide at 9--17 subjects/group to report as a fairness finding.
At $n{=}28$, subgroup gaps are not reliably resolvable.

% ---------------------------------------------------------------
\section*{Bottom line}
\begin{enumerate}[leftmargin=1.4em]
\item \textbf{Ship SegFormer-B0 distilled} --- matches the B2 teacher's
  accuracy ($\Delta$ \ns) at 2$\times$ the speed and 7$\times$ fewer params,
  and never blanks (0/185).
\item \textbf{Keep B2 teacher} as the distillation source and a model that also
  never blanks (0/185).
\item \textbf{YOLO} is 2$\times$ faster / 7$\times$ smaller but blanks on
  2--6\,\% of images $\to$ risky for injury documentation despite a competitive
  median. If reported, lead with \textbf{miss rate}, not Dice.
\item \textbf{Model differences are label-limited:} at $n{=}28$ subjects, the
  only resolvable accuracy signals are the miss rate and the SegFormer-vs-YOLO
  gap; healthy-model Dice differences are null.
\end{enumerate}

\end{document}
